A Switching Planner for Combined Task and Observation Planning

### 2010-11-21 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Few tiny mistakes from yesterday.
 - Charles

\noindent Where $b_t$ is the belief state at time $t$. Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (i.e., conformant) and contingent plans.

@@

The syntax and semantics for describing initial state distributions in
DTPDDL is taken verbatim from PPDDL. It is useful to present that
factored tree-like structure here, in order to aid our discussion of
sequential planning in POMDP determinisations. The distribution is
expressed in a tree-like structure of terms. Each term is either: (1)
atomic, e.g., $(=(\pp{location}~\pp{box})~\pp{office})$, (2)
probabilistic, e.g., $(\pp{probabilistic}~p_1 (T_1) .. p_n (T_n))$
where $T_i$ are conjunctive, or (3) a conjunct over probabilistic and
atomic terms. The root term is always conjunctive, and the leaves are
atomic. For example, the starting distribution for $\pp{R2D2}$ might
be described thusly:

@@

\noindent The interpretation of such an expression can be given
according to a recursive note of {\em visiting} terms. Here, an atom
is visited if its conjunctive parent is visited, and a conjunctive
term is visited if all its immediate subterms are visited. A
probabilistic term is visited if exactly one of its subterms, $T_i$,
is visited. Each valid visitation of the root term according to this
recursive definition encapsulates a starting state, along with the
probability it occurs. The former corresponds to the union of all
visited atoms, and the latter corresponds to the product of $p_i$
entries on the visited subterms of probabilistic elements. Making
these ideas concrete, our example yields the following flat state
distribution:

>>>>

\noindent Where $b_t$ is the belief state at time $t$. Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (e.g., conformant) and contingent plans.

@@

The syntax and semantics for describing initial state distributions in
DTPDDL is taken verbatim from PPDDL. It is useful to present that
factored tree-like structure here, in order to aid us when discussing
sequential planning in POMDP determinisations. The distribution is
expressed in a tree-like structure of terms. Each term is either: (1)
atomic, e.g., $(=(\pp{location}~\pp{box})~\pp{office})$, (2)
probabilistic, e.g., $(\pp{probabilistic}~p_1 (T_1) .. p_n (T_n))$
where $T_i$ are conjunctive, or (3) a conjunct over probabilistic and
atomic terms. The root term is always conjunctive, and the leaves are
atomic. For example, the starting distribution for $\pp{R2D2}$ might
be described thusly:

@@

\noindent The interpretation of such an expression can be given
according to a recursive notion of {\em visitation} over terms. Here,
an atom is {\em visited} if its conjunctive parent is visited, and a
conjunctive term is visited if all its immediate subterms are
visited. A probabilistic term is visited if exactly one of its
subterms, $T_i$, is visited. Each valid visitation of the root term
according to this recursive definition encapsulates a starting state,
along with the probability it occurs. The former corresponds to the
union of all visited atoms, and the latter corresponds to the product
of $p_i$ entries on the visited subterms of probabilistic
elements. Making these ideas concrete, our example yields the
following flat state distribution:
